Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-20 paper/paper.tex
Add and remove references for the background section #51
Correct typos in the reference section #56

\bibitem{} Besley, Timothy, and Torsten Persson. 2011. \textit{Pillars of Prosperity : The Political Economics of Development Clusters}. Princeton University Press.

@@

\bibitem{} Cameron, A. Colin, Jonah B. Gelbach, and Douglas L. Miller. 2011. ``Robust Inference With Multiway Clustering.'' \textit{Journal of Business \& Economic Statistics}, 29(2): 238--249.
\bibitem{} Casey, K., R. Glennerster, and E. Miguel. 2012. ``Reshaping Institutions: Evidence on Aid Impacts Using a Preanalysis Plan.'' \textit{The Quarterly Journal of Economics}, 127(4): 1755--1812.

@@

\bibitem{} Caspersen, Nina. 2012. \textit{Unrecognized States : The Struggle for Sovereignty in the Modern International System}. Cambridge: Polity Press.

@@

\bibitem{} Dawisha, Karen. 2014. \textit{Putin?s Kleptocracy : Who Owns Russia?}. New York: Simon and Schuster.
\bibitem{} Dell, Melissa. 2010. ``The Persistent Effects of Peru?s Mining Mita.'' \textit{Econometrica}, 78(6): 1863--1903.

@@

\bibitem{} Dreher, Axel, Andreas Fuchs, Roland Hodler, Bradley C. Parks, Paul A. Raschky, and Michael J. Tierney. 2015. ``Aid on Demand: African Leaders and the Geography of China?s Foreign Assistance.'' CEPR Discussion Paper, 10170.

@@

@@

\bibitem{} GADM. 2018. ``GADM Maps and Data (version 3.6).'' \verb!gadm.org! (accessed February 7, 2019).

@@

\bibitem{} International Crisis Group. 2004. ``Georgia: Avoiding War in South Ossetia.'' ICG Europe Report, no.\ 159.

@@

\bibitem{} King, Charles. 2000. \textit{The Moldovans : Romania, Russia, and the Politics of Culture}. Hoover Institution Press.
\bibitem{} King, Charles. 2001. ``The Benefits of Ethnic War: Understanding Eurasia?s Unrecognized States.'' \textit{World Politics}, 53(04): 524--552.

@@

\bibitem{} Pinkovskiy, Maxim, and Xavier Sala-i-Martin. 2016. ``Newer Need Not be Better: Evaluating the Penn World Tables and the World Development Indicators Using Nighttime Lights.''. NBER Working Paper, 22216.

@@

\bibitem{} Smolnik, Franziska. 2016. \textit{Secessionist Rule : Protracted Conflict and Configurations of Non-State Authority}. Frankfurt: Campus Verlag
\bibitem{} Storeygard, Adam. 2016. ``Farther on down the Road: Transport Costs, Trade and Urban Growth in Sub-Saharan Africa.'' \textit{The Review of Economic Studies}, 83(3): 1263--1295.

@@

\bibitem{} Toal, Gerard. 2008. ``Russia?s Kosovo: A Critical Geopolitics of the August 2008 War over South Ossetia.'' \textit{Eurasian Geography and Economics}, 49(6): 670--705.
\bibitem{} Toal, Gerard, and John O?Loughlin. 2017. ``Frozen Fragments, Simmering Spaces: The Post-Soviet De Facto States.'' in Holland, Edward C., and Matthew Derrick (Eds.), \textit{Questioning Post-Soviet}. Washington DC: Woodrow Wilson Press, pp. 103--125.

@@

\bibitem{} Witmer, Frank D.W., and John O?Loughlin. 2011. ``Detecting the Effects of Wars in the Caucasus Regions of Russia and Georgia Using Radiometrically Normalized DMSP-OLS Nighttime Lights Imagery.'' \textit{GIScience \& Remote Sensing}, 48(4): 478--500.

>>>>

\bibitem{} Besley, Timothy, and Torsten Persson. 2011. \textit{Pillars of Prosperity: The Political Economics of Development Clusters}. Princeton University Press.

@@

\bibitem{} Cameron, A. Colin, Jonah B. Gelbach, and Douglas L. Miller. 2011. ``Robust Inference with Multiway Clustering.'' \textit{Journal of Business \& Economic Statistics}, 29(2): 238--249.
\bibitem{} Casey, K., R. Glennerster, and E. Miguel. 2012. ``Reshaping Institutions: Evidence on Aid Impacts Using a Preanalysis Plan.'' \textit{Quarterly Journal of Economics}, 127(4): 1755--1812.

@@

\bibitem{} Caspersen, Nina. 2012. \textit{Unrecognized States: The Struggle for Sovereignty in the Modern International System}. Cambridge: Polity Press.

@@

\bibitem{} Dawisha, Karen. 2014. \textit{Putin's Kleptocracy : Who Owns Russia?}. New York: Simon and Schuster.
\bibitem{} Dell, Melissa. 2010. ``The Persistent Effects of Peru's Mining Mita.'' \textit{Econometrica}, 78(6): 1863--1903.

@@

\bibitem{} Dreher, Axel, Andreas Fuchs, Roland Hodler, Bradley C. Parks, Paul A. Raschky, and Michael J. Tierney. 2015. ``Aid on Demand: African Leaders and the Geography of China's Foreign Assistance.'' CEPR Discussion Paper, 10170.

@@

\bibitem{} Freedom House 2006. ``Abkhazia.'' \textit{Freedom in the World 2006}. \verb!freedomhouse.org/report/freedom-world/2006/abkhazia! (accessed on 20 March 2019).

@@

\bibitem{} GADM. 2018. \textit{GADM Maps and Data} (version 3.6). \verb!gadm.org! (accessed February 7, 2019).

@@

@@

\bibitem{} King, Charles. 2000. \textit{The Moldovans : Romania, Russia, and the Politics of Culture}. Stanford: Hoover Institution Press.
\bibitem{} King, Charles. 2001. ``The Benefits of Ethnic War: Understanding Eurasia's Unrecognized States.'' \textit{World Politics}, 53(04): 524--552.

@@

\bibitem{} Pinkovskiy, Maxim, and Xavier Sala-i-Martin. 2016. ``Newer Need Not be Better: Evaluating the Penn World Tables and the World Development Indicators Using Nighttime Lights.'' NBER Working Paper, 22216.

@@

\bibitem{} Smolnik, Franziska. 2016. \textit{Secessionist Rule: Protracted Conflict and Configurations of Non-State Authority}. Frankfurt: Campus Verlag.
\bibitem{} Storeygard, Adam. 2016. ``Farther on down the Road: Transport Costs, Trade and Urban Growth in Sub-Saharan Africa.'' \textit{Review of Economic Studies}, 83(3): 1263--1295.

@@

\bibitem{} Toal, Gerard. 2008. ``Russia's Kosovo: A Critical Geopolitics of the August 2008 War over South Ossetia.'' \textit{Eurasian Geography and Economics}, 49(6): 670--705.
\bibitem{} Toal, Gerard, and John O'Loughlin. 2017. ``Frozen Fragments, Simmering Spaces: The Post-Soviet De Facto States.'' in Holland, Edward C., and Matthew Derrick (Eds.), \textit{Questioning Post-Soviet}. Washington DC: Woodrow Wilson Press: 103--125.

@@

\bibitem{} Witmer, Frank D.W., and John O'Loughlin. 2011. ``Detecting the Effects of Wars in the Caucasus Regions of Russia and Georgia Using Radiometrically Normalized DMSP-OLS Nighttime Lights Imagery.'' \textit{GIScience \& Remote Sensing}, 48(4): 478--500.
